\section{Introduction}
\label{sec:intro}

%1. Why UQ is important for this problem?
%2. Challenges pertaining to UQ. Include a table for exponential scaling. 
%3. What has been done in previous UQ studies for atomistic level simulations.
%4. How we tried to address the challenge in our previous work.
%5. How is this work different?
%6. Key contributions.
%7. Organization of the paper.

Non-equilibrium molecular dynamics (NEMD) simulations are commonly used to investigate
bulk thermal conductivity of non-metallic elements such as carbon, silicon, and
germanium~\cite{Dumitrica:2010}. The system is subjected to either a heat flux or a temperature
gradient by means of thermostatting. Resulting steady-state temperature gradient in the
former and heat exchange between the thermostats in the latter is recored. The thermal
conductivity at a given system size is hence estimated using Fourier's law. In the
so-called direct method~\cite{Schelling:2002,Turney:2009,Zhou:2009,Landry:2009,
McGaughey:2006,Ni:2009,Shi:2009,Wang:2009,Papanikolaou:2008},
the thermal conductivity is estimated at multiple values of the
system size. The inverse of thermal conductivity ($\kappa^{-1}$) is plotted against the inverse of 
system size ($L^{-1}$) and a linear extrapolation procedure is used to estimate the y-intercept
of the plot. Inverse of the y-intercept is regarded as the bulk thermal conductivity
of the system since it corresponds to an infinitely large system (in theory). 

Although widely used, severe limitations are associated with the direct method.
The validity of the linear extrapolation procedure is not well established. Recent
investigations have revealed the existence of a non-linear trend in the $\kappa^{-1}$-$L^{-1}$
relationship especially at large values of $L$~\cite{Sellan:2010} for Si. Additionally, 
thermal conductivity estimate for a given size depends upon the choice of a potential
function and associated values of its parameters. Specifically for Si, the Stillinger-Weber (SW)
inter-atomic potential is commonly used for a wide variety of applications:
%
\be
\Phi = \sum\limits_{i,j(i<j)}\phi_2(A,B,p,q,\alpha)\hspace{1mm}+\sum\limits_{i,j,k(i<j<k)}\phi_3(\lambda,\gamma)
\ee
%
However, according
to the methodology presented by Stillinger and Weber in~\cite{Stillinger:1985},
the following shortcomings must be noted:
%
\begin{itemize}
\item The SW potential function accounts for the second-order ($\phi_2$) and
third-order ($\phi_3$) atomic 
interactions. However, this representation can be inadequate in situations where 
higher order interactions become significant.  
\item Nominal values of the SW potential parameters were estimated using a 
limited search in a 7-dimensional parameter space. Regression-based parameter
estimates relied on the available set of experimental data while ensuring structural
stability. Hence, the estimates are tightly coupled with the set of data used for
calibration, and did not account for the presence of measurement uncertainty. 
\item Noise inherent in MD predictions can also be significant and
was not accounted for in the analysis. 
\end{itemize}
%
Hence, using the same set of nominal values for a wide range of Si-based systems and
applications is not ideal. It is therefore important to attribute uncertainty to the values and
investigate its impact on NEMD predictions. 

This paper aims to present a computational framework aimed at dimension reduction
for enabling the propagation of uncertainty from the SW potential parameters to the
quantity of interest (QoI) i.e. the thermal conductivity of a Si bar in an efficient manner. The
motivation for input-space dimension reduction stems from exponential scaling in
computational effort with the number of parameters, illustrated using the following
table:
%
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
\begin{table}[htbp]
\centering
\ra{1.3}
\begin{tabular}{@{}ccc@{}}\toprule
Parameters & Model Runs & Time (1h/run)\\
\bottomrule
1 & 10 & 10 hours \\
2 & 10$^2$ & 4.2 days \\
3 & 10$^3$ & 1.4 months \\
4 & 10$^4$ & 1.2 years \\
5 & 10$^5$ & 11.6 years \\
6 & 10$^6$ & 115.7 years \\
7 & 10$^7$ & 1157.41 years \\
\bottomrule
\end{tabular}
\caption{Exponential scaling of computational effort with the number of uncertain parameters.}
\end{table}
%
In the above table, we consider that in order to perform UQ, an average of 10 runs along each input dimension
is needed, and each run takes approximately an hour. We can easily compute that the time required to 
perform the analysis in a 7-dimensional input space is in the $\mathcal{O}(10^3)$ years which makes it
intractable. Note that the considered compute times do not account for simulation queue times that 
increases the time required for a run. 
Although computational gains can be realized using parallel computations and sparse grids
for efficient surrogate construction~\cite{Ma:2009,Constantine:2012,Petvipusit:2014,Vohra:2014}, 
the issue of exponential scaling would persist.  
Hence, we aim to tackle this issue by focussing our efforts on reducing the dimensionality of the problem
which is expect to yield maximum gains. In our earlier efforts, we presented a strategy~\cite{Vohra:2018b}
for constructing a surrogate for thermal conductivity using NEMD predictions and their dependence
on the SW potential parameters in a reduced space, evaluated using the derivative-based global sensitivity measures
(DGSMs)~\cite{Vohra:2018a}. The focus was therefore on determining the relative importance of the
parameters and fixing the unimportant parameters at their nominal values. On the other hand, the
framework presented in this study aims to identify key directions in the input space along which the
QoI predominantly varies. The set of directions constitute the so-called 
\textit{active subspace}~\cite{Constantine:2015}.  

The active subspace methodology relies on estimating the partial derivative of the QoI 
with respect to each uncertain input. This requirement poses a couple of limitations on its
applicability: (1) The QoI is required to be differentiable in the considered input domain, and (2)
In most complex problems, the derivative needs to be approximated using numerical techniques
which require model evaluations and thus impose computational burden. Fortunately, in this case,
the thermal conductivity is observed to exhibit a smooth dependence on the SW parameters. 
To mitigate the challenge pertaining to derivative estimation, we exploit our recent experience
involving the application of a gradient-free approach for evaluating the active subspace in
chemical kinetics applications~\cite{Vohra:2018c}. In this approach, the gradient is estimated
using a regression-based local linear approximation of the QoI and hence does not require
model evaluations. It was shown in~\cite{Vohra:2018c} that the gradient-free approach is
remarkably accurate is estimate the mean and the mode value of the uncertain QoI. However,
it did not fully capture the sensitivity associated with all uncertain inputs. Since our focus
in this study is on uncertainty propagation from inputs to the QoI, the gradient-free approach
seems like a suitable choice considering the computational effort associated with model 
evaluation for thermal conductivity of a Si bar. In fact, our findings reveal the existence of a 
1-dimensional active subspace in this case indicating enormous scope for computational savings.
Moreover, the global sensitivity measures based
on the active subspace are found to be consistent with our earlier estimates based on DGSMs. 

The remainder of this article is organized as follows. In section~\ref{sec:bg}, we provide details
pertaining to the NEMD simulation in \ref{sub:nemd}, and brief background on active subspaces
in~\ref{sub:as}. Details pertaining to the computational methodology are
provided in section~\ref{sec:method}. Results based on the active subspace methodology
implemented including verification of the reduced-space surrogate, and sensitivity analysis
are presented in section~\ref{sec:results}. Finally, we draw useful conclusions based on this
work in section~\ref{sec:conc}.
































